Preliminary Draft

### 2021-07-27 article/draft.tex
updates in discussion + twitter code

Misinformation specific interventions by mainstream platforms are hard to monitor, study or verify by third parties (e.g. academic community, data journalists, NGOs), as in many cases misleading or false content does not qualify as a violation of a given platform's rules and it does not explicitly appear as a separate category in available transparency reports. This makes the study of online misinformation, the assessment of the impact of platforms' actions to tackle misinformation and their relevancy a burdensome task for the academic community. Hence, in the present article we explain how to verify with data mining mainstream platforms' current actions regarding content with low credibility or false information. We do so by providing a series of examples for different interventions and platforms. We chose to focus on three platforms: Facebook, Twitter and YouTube. Both Facebook and YouTube are in the top three most popular social media platforms in terms of number of users.\footnote{See for example the ranking of the most popular social networks as of April 2021 on Statista: \href{https://www.statista.com/statistics/272014/global-social-networks-ranked-by-number-of-users/}{https://www.statista.com/statistics/272014/global-social-networks-ranked-by-number-of-users/}.} We further choose Twitter because it is a social networking platform with the most news-focused users, according to the Pew Research center (2019)~\cite{pew1}. To collect data from these three platforms, we either used the APIs (Application Programming Interfaces), or web scraping, i.e. retro-engineering the HMTL code of a web page to extract meaningful data, see Table \ref{tab1} for a summary. Minet \cite{minet}, a webmining tool developed by the Médialab SciencesPo, was often used, and we scripted our own data mining code when it was necessary.

@@

		%To facilitate the verification in the policy applications, we would generally recommend for the platforms to be more transparent. But too much transparency on how the regulation policies are exactly implemented can actually backfire. For example YouTube is certainly applying an 'information' banner on all videos mentioning COVID-19 and related terms in their title. Misinformation accounts are trying to avoid the official banners by using terms as 'C.O.V.I.D' or 'C O V I D'. If YouTube was totally transparent on that matter and published the list of 'dangerous' words that leads to an information banner, this list would of course help us to understand YouTube's policies but it would also help the misinformation actors to escape the regulation. There is thus a balance between communicating enough so the public can know precisely how the platforms are regulating their content, but without giving too much information that would allow the policies to be bypassed.

@@

{\bf Lack of misinformation specific interventions.}

@@

>>>>

Misinformation related interventions by mainstream platforms are hard to monitor, study or verify by third parties (e.g. academic community, data journalists, NGOs), as in many cases misleading or false content does not qualify as a violation of a given platform's rules and it does not explicitly appear as a separate category in available transparency reports. This makes the study of online misinformation, the assessment of the impact of platforms' actions to tackle misinformation and their relevancy a burdensome task for the academic community. Hence, in the present article we explain how to verify with data mining mainstream platforms' current actions regarding content with low credibility or false information. We do so by providing a series of examples for different interventions and platforms. We chose to focus on three platforms: Facebook, Twitter and YouTube. Both Facebook and YouTube are in the top three most popular social media platforms in terms of number of users.\footnote{See for example the ranking of the most popular social networks as of April 2021 on Statista: \href{https://www.statista.com/statistics/272014/global-social-networks-ranked-by-number-of-users/}{https://www.statista.com/statistics/272014/global-social-networks-ranked-by-number-of-users/}.} We further choose Twitter because it is a social networking platform with the most news-focused users, according to the Pew Research center (2019)~\cite{pew1}. To collect data from these three platforms, we either used the APIs (Application Programming Interfaces), or web scraping, i.e. retro-engineering the HMTL code of a web page to extract meaningful data, see Table \ref{tab1} for a summary. Minet \cite{minet}, a webmining tool developed by the Médialab SciencesPo, was often used, and we scripted our own data mining code when it was necessary.

@@

@@

{\bf Lack of misinformation specific interventions.} It is likely that most interventions related to misinformation correspond to interventions that were designed for other policy areas. To illustrate, YouTube explicitly states that: {\it Several policies in our Community Guidelines are directly applicable to misinformation}; such as deceptive practices, impersonation and hate speech policy.

@@

% points to make ? argument ? en gros, interventions existaient dejà on les utilise pour la mesinformation, la mesinformation n'est pas officiellemtn
